Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-11 ltx/data_paper/DataPaper.tex
edit to introduction

\section{Introduction}
\begin{itemize}
	\item Understanding of macroscopic neurodynamics
	\item Neural field model
	\item Improvements in electrode technology with great spatiotemporal resolution
\end{itemize}
The aim of this paper is to create a patient-specific neural field model, by estimating parameters of a general mathematical model using data acquired from an epilepsy surgical candidate in a clinical setting.

@@

>>>>

\section{Introduction}
\begin{itemize}
	\item Understanding of macroscopic neurodynamics
	\item Neural field model
	\item Improvements in electrode technology with great spatiotemporal resolution

\end{itemize}
The aim of this paper is to create a patient-specific neural field model, by estimating parameters of a general mathematical model using data acquired from an epilepsy surgical candidate in a clinical setting.

@@

Another recent approach for large scale neural networks based on graph theory \cite{Albert2002,Bang-Jensen2010}, employs a realistic anatomical connectivity from CoCoMac data base \cite{Kotter2004} to model resting state activity in the brain \cite{Ghosh2008,Deco2009} where each node in the network is modelled by physiologically reasonable neural population model of their internal dynamics. They perform a stability analysis of the network in terms of total connectivity and time delayes in the presence of noise. Such approach has a potential to model a virtual brain which can incorporate data from individual patient, giving insights into how patient specific features can affect its large scale neural dynamics \cite{Jirsa2010,Deco2010}.
